---
title: "QC_RNASeq_BBRIC_count"
output: 
  pdf_document:
    toc: true
    highlight: zenburn    
---

<!--- ajout d'un saut de page apres le toc --->
\newpage

```{r echo=FALSE}


# treatment of count BBRIC file
bbric.df <- read.table(opt$count, header = TRUE, sep="\t")
nbcoltotal=dim(bbric.df)[2]
nblib=(nbcoltotal - 8)/2
rawvalues = bbric.df[, seq(9, nbcoltotal, by=2)]
colnames(rawvalues) = gsub("-count", "", colnames(rawvalues)) 
rpkmvalues = bbric.df[, seq(10, nbcoltotal, by=2)]
colnames(rpkmvalues) = gsub("-rpkm", "", colnames(rpkmvalues)) 
lograwvalues <- log(rawvalues + 1)
logrpkmvalues <- log(rpkmvalues + 1)

# treatment of design file
if (!is.null(opt$design)) {
	design.df <- read.table(opt$design, header=TRUE, sep="\t")
	lib_names <- design.df[,1]
	Factor = design.df[,2]
	moda_names = unique (Factor)
	testcol  <- colorRampPalette(c('blue','red', 'green', 'orange'))
	colmoda <- testcol(length(moda_names))
	colorModa <- c()
	for (i in 1:length(moda_names)) {
		moda = moda_names[i]
		colorModa[moda]=colmoda[i]
	}
	colorLib <- c()
	for (i in 1:length(lib_names)) {
		lib = lib_names[i]
		moda = Factor[i]
		collib = colorModa[moda]
		colorLib[lib]=collib
	}
}

```

Cluster dendrogram representing the hierarchical clustering of libraries (log raw values)
==========================================================================================
```{r echo=FALSE}
dist.lame.cor <- 1 - cor(lograwvalues, use="pairwise.complete.obs")
hc.lame.cor <- hclust(as.dist(dist.lame.cor))
dendCol <- as.dendrogram(hc.lame.cor)

if (!is.null(opt$design)) {
	labels_colors(dendCol) <- colorModa[Factor][order.dendrogram(dendCol)]
}
plot(dendCol, main= "Cluster Dendrogram (log raw values)")
```

Cluster dendrogram representing the hierarchical clustering of libraries (log rpkm values)
==========================================================================================
```{r echo=FALSE}
dist.lame.cor <- 1 - cor(logrpkmvalues, use="pairwise.complete.obs")
hc.lame.cor <- hclust(as.dist(dist.lame.cor))
dendCol <- as.dendrogram(hc.lame.cor)

if (!is.null(opt$design)) {
	labels_colors(dendCol) <- colorModa[Factor][order.dendrogram(dendCol)]
}
plot(dendCol, main= "Cluster Dendrogram (log rpkm values)")
```

PCA (Principal component analysis) of the libraries (log raw values)
===================================================================
```{r echo=FALSE}
acpnnlog = PCA(t(lograwvalues), scale.unit=FALSE, graph= FALSE)
plot(acpnnlog, axes=c(1,2), choix=c("ind"), title = "Individuals factor map (PCA) (log raw values)")
```

PCA (Principal component analysis) of the libraries (log rpkm values)
=====================================================================
```{r echo=FALSE}
acpnnlog = PCA(t(logrpkmvalues), scale.unit=FALSE, graph= FALSE)
plot(acpnnlog, axes=c(1,2), choix=c("ind"), title = "Individuals factor map (PCA) (log rpkm values)")
```

Barplot representing for each library the number of features (genes / RNA) that have at least 10 reads mapped
==============================================================================================================
```{r echo=FALSE}
vecteursup10 = c()
vecteurunionprov = c()
vecteurall = c()
for (colo in 1:nblib) { vecteursup10 <- append(vecteursup10, length(which(rawvalues[,colo]>9)))}
for (colo in 1:nblib) { vecteurunionprov <- append(vecteurunionprov, which(rawvalues[,colo]>9))}
vecteurunion = unique(vecteurunionprov)
vecteursup10 <- append(vecteursup10, length(vecteurunion))
for (colo in 1:(nblib+1)) { vecteurall <- append(vecteurall, length(rawvalues[,1]))}

if (!is.null(opt$design)) {
	barplot(vecteursup10, names.arg=c(colnames(rawvalues[1:nblib]), "At least in 1 lib"), las=2, cex.names=0.7, col=c(colorLib, "black"), ylim=c(0,max(vecteurall)))
} else {
	barplot(vecteursup10, names.arg=c(colnames(rawvalues[1:nblib]), "At least in 1 lib"), las=2, cex.names=0.7, ylim=c(0,max(vecteurall)))
}

todisplay = data.frame(c(colnames(rawvalues[1:nblib]), "At least in 1 lib"),vecteursup10, vecteurall)
names(todisplay) = c('lib', 'nb features with at least 10 reads', 'nb features total')
todisplay[,1:3]

```

Box-plot (log raw values)
=========================
```{r echo=FALSE}
if (!is.null(opt$design)) {
	boxplot(lograwvalues, las=2, cex.axis=0.7, main="BoxPlot of log (raw counts)", col=colorLib)
} else {
	boxplot(lograwvalues, las=2, cex.axis=0.7, main="BoxPlot of log (raw counts)")
}
```

Box-plot (log rpkm values)
============================
```{r echo=FALSE}
if (!is.null(opt$design)) {
	boxplot(logrpkmvalues, las=2, cex.axis=0.7, main="BoxPlot of log (rpkm counts)", col=colorLib)
} else {
	boxplot(logrpkmvalues, las=2, cex.axis=0.7, main="BoxPlot of log (rpkm counts)")
}
```

Summary of raw values
============================

```{r echo=FALSE}
summary(rawvalues)
```

Summary of rpkm values
============================
```{r echo=FALSE}
summary(rpkmvalues)
```