---
title: "QC_RNASeq_generic_count"
output: 
  pdf_document:
    toc: true
    highlight: zenburn    
---

<!--- ajout d'un saut de page apres le toc --->
\newpage


```{r echo=FALSE}


# treatment of generic file
generic.df <- read.table(opt$count, header = TRUE, sep="\t", check.names=FALSE)
nbcol=dim(generic.df)[2]
nblib=nbcol - 1
values <- generic.df[,2:nbcol]
logvalues <- log(generic.df[,2:nbcol] + 1)

# treatment of design file
if (!is.null(opt$design)) {
	design.df <- read.table(opt$design, header=TRUE, sep="\t", check.names=FALSE)
	lib_names <- design.df[,1]
	Factor = design.df[,2]
	moda_names = unique (Factor)
	testcol  <- colorRampPalette(c('blue','red', 'green', 'orange'))
	colmoda <- testcol(length(moda_names))
	colorModa <- c()
	for (i in 1:length(moda_names)) {
		moda = moda_names[i]
		colorModa[moda]=colmoda[i]
	}
	colorLib <- c()
	for (i in 1:length(lib_names)) {
		lib = lib_names[i]
		moda = Factor[i]
		collib = colorModa[moda]
		colorLib[lib]=collib
	}
}

```

Cluster dendrogram representing the hierarchical clustering of libraries (log values)
==========================================================================================
Input Data = RNASeq count expression file.

After a log transformation and a Pearson correlation, data are submitted to an Ascending Hierarchical Clustering (AHC) (Ward).

The aim of AHC is to cluster the libraries, based on their count values.

Expected results :

-	All the replicates for an experimental condition should cluster together

-	The different experimental conditions should be well separated

Application :

-	Estimate the distance between the different libraries

-	Detect problems of sample inversion

```{r echo=FALSE}
dist.lame.cor <- 1 - cor(logvalues, use="pairwise.complete.obs")
hc.lame.cor <- hclust(as.dist(dist.lame.cor))
dendCol <- as.dendrogram(hc.lame.cor)

if (!is.null(opt$design)) {
	labels_colors(dendCol) <- colorModa[Factor][order.dendrogram(dendCol)]
}
plot(dendCol, main= "Cluster Dendrogram (log values)")
```
\newpage

Barplot representing for each library the number of features (genes / RNA) that have at least 10 reads mapped
==============================================================================================================
For each library, the number of genes that have at least 10 reads mapped, is displayed.

The number of 10 is empirical, and was chosen because we think that it is the minimal number required to consider that a feature is expressed.

Expected results :

-	All the libraries should have quite the same number of genes with >= 10 reads mapped

Application :

-	Estimate the number of genes usable / library

-	Estimate the number of valid genes (Number of features with at least 10 reads mapped, in at least 1 lib)

-	Check that the mapping parameters and structural annotation file are adequate for all the libraries (including samples that do not come from the reference genome)


```{r echo=FALSE}
vecteursup10 = c()
vecteurunionprov = c()
vecteurall = c()
for (colo in 1:nblib) { vecteursup10 <- append(vecteursup10, length(which(values[,colo]>9)))}
for (colo in 1:nblib) { vecteurunionprov <- append(vecteurunionprov, which(values[,colo]>9))}
vecteurunion = unique(vecteurunionprov)
vecteursup10 <- append(vecteursup10, length(vecteurunion))
for (colo in 1:nbcol) { vecteurall <- append(vecteurall, length(values[,1]))}

if (!is.null(opt$design)) {
	barplot(vecteursup10, names.arg=c(colnames(values[1:nblib]), "At least in 1 lib"), las=2, cex.names=0.7, col=c(colorLib, "black"), ylim=c(0,max(vecteurall)))
} else {
	barplot(vecteursup10, names.arg=c(colnames(values[1:nblib]), "At least in 1 lib"), las=2, cex.names=0.7, ylim=c(0,max(vecteurall)))
}

todisplay = data.frame(c(colnames(values[1:nblib]), "At least in 1 lib"),vecteursup10, vecteurall)
names(todisplay) = c('lib', 'nb features with at least 10 reads', 'nb features total')
todisplay[,1:3]

 ```
 \newpage
 
 Box-plot (log values)
=========================
Input Data = RNASeq count expression file.

For each library, box-plots of log (count values) are displayed.

Expected results :

-	All the libraries should have quite the same distribution

Application :

-	Ensure that all the libraries have quite the same distribution to initiate a powerful differential expression analysis

-	Check that an unexpected clustering in the AHC (first graph) is not caused by a heterogeneous distribution between libraries

```{r echo=FALSE}
if (!is.null(opt$design)) {
	boxplot(logvalues, cex.axis=0.7, las=2, main="BoxPlot of log(count)", col=colorLib)
} else {
	boxplot(logvalues, cex.axis=0.7, las=2, main="BoxPlot of log(count)")
}
```
\newpage

Summary of values
============================

```{r echo=FALSE}
summary(values)
```
